\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2018-01-08 HOPS/photometry/ms.tex

\section{Discussion}
\label{sec:discussion}
\par
The results presented in Section~\ref{sec-results} show the global properties of the HOPS protostar sample.  Since the sub-regions in Orion~A and B are well stratified by declination, differences are easily explored by using declination as a proxy for sub-region.   Indeed, Figures~\ref{fig:mdFlux_v_dec},~\ref{fig:clr1_v_dec},~\&~\ref{fig:clr2_v_dec} show that systematic variations exist in the observed proto-stellar properties as a function of declination in the Orion~A~\&~B clouds.  We discuss in Sections~\ref{sec:compbias}~\&~\ref{sec:popdiff} two explanations of this observed trend.   Again, we will restrict ourselves to observed quantities only and leave the detailed exploration of inferred properties to companion papers.

@@

\subsection{Population differences}
\label{sec:popdiff}
\par
We also consider the implications if the correlations shown in Figure~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} are due to systematic differences in the observed population as a function of sub-region.  \cite{ali} show that \herschel\ colors become redder with increasing envelope mass (envelope accretion rate).  In fact, the envelope infall rate is the dominating factor in setting colors.  We rule out inclination as a factor because no reasonable justification can be made for systematic differences in inclination as a function of sub-region in Orion.  Thus, we focus on differences in envelope properties.  When interpreted as such, Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}  imply that either the accretion process is different amongst the sub-regions, or that the protostars are at systematically different stages of development in each sub-region.   Both scenarios thereby conspire to lead to systematic differences in the envelope properties of the protostars.
\par
If we surmise that the accretion process is the leading cause, then there are two means to achieve this end: (i) the available gas and dust contributing to the envelope is systematically different between the sub-regions, or (ii) the central cores are systematically more massive in regions with redder colors.  Both scenarios may, in fact, point to simply having higher gas+dust densities and higher gas+dust content to explain redder colors.  We conclude that the observed properties of \herschel-detected protostars in Orion are consistent with predicted differences in populations implied by differences in gas column densities and star-formation scenarios in the region.
\par
Alternatively, regions with higher density may speed up protostellar evolution because collapse time-scales are dependent on the local density of material.  Thus, the observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} may be viewed as differences in the evolutionary status of the protostars.  To explain the trend, the protostars in the Orion OMC-2/3 and ONC sub-regions are required to have transferred more of their mass in the central cores, which leads to more accretion and higher infall rates.  While similar to differences in the accretion processes, this scenarios suggests a fundamental difference in the star-formation process itself between sub-regions.

>>>>

\section{Discussion}
\label{sec:discussion}
\par
The results presented in Section~\ref{sec-results} show the global properties of the HOPS protostar sample.  Since the sub-regions in Orion~A and B are well stratified by declination, differences are easily explored by using declination as a proxy for sub-region.   Indeed, Figures~\ref{fig:mdFlux_v_dec},~\ref{fig:clr1_v_dec},~\&~\ref{fig:clr2_v_dec} show that systematic variations exist in the observed proto-stellar properties as a function of declination in the Orion~A~\&~B clouds.  We discuss in Sections~\ref{sec:compbias}~\&~\ref{sec:popdiff} two explanations of this observed trend.   Again, we will restrict ourselves to observed quantities only and leave the detailed exploration of inferred properties to companion papers.  We rule out inclination angle (to the observer) as a factor because no reasonable justification can be made for systematic differences in inclination as a function of sub-region in Orion.

@@

\subsection{Population differences}
\label{sec:popdiff}
\par
We also consider systematic differences in the underlying protostar population as a possible cause for the observed correlations in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}.  \cite{ali} show that \herschel\ colors are highly correlated with the assumed envelope properties, especially, the infall rate and the envelope mass. In fact, \cite{ali} find protostellar envelopes to be the dominant factor affecting the observed colors in the \herschel\ bands.  Thus, if the correlations in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} reflect actual population differences in the subregions, then the envelope properties are likely to be the actual underlying cause of said differences.
\par
One explanation for this difference is that the protostars are, simply, at different stages of development in each sub-region.  The observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec} may then be viewed as differences in the evolutionary epoch of the protostars.  To further explain the trend, the protostars in the Orion OMC-2/3 and ONC sub-regions are required, in this scenario, to have transferred more of their mass in the central cores to be consistent with their redder colors.  If we assume that the fundamental star-formation process responsible for the protostellar evolution is the same across the sub-regions, then the systematic differences in the evolutionary epochs of the protostars could have come from differences in the onset of the start-formation itself.  Alternatively, the sub-regions with higher local gas+dust density may speed up protostellar evolution because free-fall collapse time-scales are dependent on the local density of material.  Or, the availability of gas and dust contributing to the envelope is systematically different between the sub-regions.  Finally, the central cores may be systematically more massive in regions with redder colors because of actual differences in the local gas+dust content and/or the accretion process itself.
\par
Unfortunately, we lack the data needed to definitively identify which of the above scenarios (or something else entirely) may be responsible for the observed trends in Figures~\ref{fig:clr1_v_dec}~\&~\ref{fig:clr2_v_dec}, if said trend is produced by differences in the population of protostars in each subregion.  Future work combining detailed studies of the local gas+dust content may provide additional constraints.  However, we also cannot rule out that the protostars in the sub-regions were led to different evolutionary states by some fundamental and unknown difference in the star-formation process itself.
